Analyzing the Effect of Surface in Tennis Grand Slams

### 2018-09-10 contest/surface-type/paper-tennis.tex
Merging

  \title{Analyzing the Effect of Surface in Tennis Grand Slams}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Kayla Frisoli, Shannon Gallagher, and Amanda Luby}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{September 08, 2018}

@@

\hypertarget{sec:iintro}{%
\section{Introduction}\label{sec:iintro}}

@@

\hypertarget{sec:data-eda}{%
\section{Data and EDA}\label{sec:data-eda}}

\hypertarget{sec:data}{%
\subsection{Data}\label{sec:data}}

@@

\rowcolors{2}{gray!6}{white}
\begin{table}

\caption{\label{tab:tab-data}\label{tab:data}Example of the grand slam data.  It includes winner and loser attributes, match attributes, and tournament attributes.  Not all attributes are shown here.}
\centering
\begin{tabular}[t]{lrlrlrrl}
\hiderowcolors
\toprule
Tournament & Year & W. Country & W. Points & Winner & W. Rank & L. Points & Loser\\
\midrule
\showrowcolors
US Open & 2014 & USA & 58 & Serena Williams & 1 & 31 & Taylor Townsend\\
US Open & 2013 & ESP & 136 & Rafael Nadal & 2 & 112 & Philipp Kohlschreiber\\
Australian Open & 2015 & ESP & 91 & Rafael Nadal & 3 & 51 & Mikhail Youzhny\\
US Open & 2013 & USA & 65 & Serena Williams & 1 & 41 & Yaroslava Shvedova\\
Australian Open & 2017 & USA & 73 & Serena Williams & 2 & 60 & Lucie Safarova\\
\bottomrule
\end{tabular}
\end{table}
\rowcolors{2}{white}{white}

The data is obtained from Jeff Sackman's open website {[}cite{]} via the
\texttt{R} package \texttt{deuce} {[}cite{]}. All steps of our analysis
from collection to dissemination are freely available online and are
compiled into an \texttt{R} package
\url{http://github.com/shannong19/courtsports}. The paper itself may be
generated from the file
\url{https://github.com/shannong19/courtsports/blob/master/contest/surface-type/paper-tennis.Rmd}.

\hypertarget{sec:eda}{%
\subsection{Early Data Analysis}\label{sec:eda}}

\hypertarget{sec:methods}{%
\section{Methods}\label{sec:methods}}

\hypertarget{sec:results}{%
\section{Results}\label{sec:results}}

\hypertarget{sec:discussion}{%
\section{Discussion}\label{sec:discussion}}

\hypertarget{sec:refs}{%
\section{References}\label{sec:refs}}

>>>>

  \title{Analyzing the Effect of Surface in Tennis Grand Slams}
    \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
    \author{Kayla Frisoli, Shannon Gallagher, and Amanda Luby}
    \preauthor{\centering\large\emph}
  \postauthor{\par}
      \predate{\centering\large\emph}
  \postdate{\par}
    \date{September 09, 2018}

@@

{
\setcounter{tocdepth}{2}
\tableofcontents
}
\section{Introduction}\label{sec:iintro}

@@

\section{Data and EDA}\label{sec:data-eda}

\hypertarget{sec:data}{\subsection{Data}\label{sec:data}}

@@

\rowcolors{2}{gray!6}{white}

\begin{table}

\caption{\label{tab:tab-data}\label{tab:data}Example of the grand slam data.  It includes winner and loser attributes, match attributes, and tournament attributes.  Not all attributes are shown here.}
\centering
\begin{tabular}[t]{lrlrlrrl}
\hiderowcolors
\toprule
Tournament & Year & W. Country & W. Points & Winner & W. Rank & L. Points & Loser\\
\midrule
\showrowcolors
US Open & 2014 & USA & 58 & Serena Williams & 1 & 31 & Taylor Townsend\\
US Open & 2013 & ESP & 136 & Rafael Nadal & 2 & 112 & Philipp Kohlschreiber\\
Australian Open & 2015 & ESP & 91 & Rafael Nadal & 3 & 51 & Mikhail Youzhny\\
US Open & 2013 & USA & 65 & Serena Williams & 1 & 41 & Yaroslava Shvedova\\
Australian Open & 2017 & USA & 73 & Serena Williams & 2 & 60 & Lucie Safarova\\
\bottomrule
\end{tabular}
\end{table}

\rowcolors{2}{white}{white}

The data is obtained from Jeff Sackman's open website {[}cite{]} via the
\texttt{R} package \texttt{deuce} {[}cite{]}. All steps of our analysis
from collection to dissemination are freely available online and are
compiled into an \texttt{R} package
\url{http://github.com/shannong19/courtsports}.

\hypertarget{sec:eda}{\subsection{Early Data Analysis}\label{sec:eda}}

\hypertarget{sec:methods}{\section{Methods}\label{sec:methods}}

\hypertarget{sec:results}{\section{Results}\label{sec:results}}

\section{Discussion}\label{sec:discussion}

\section{References}\label{sec:refs}
